%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {web developer intern} % Job title
    {Fortinet Inc.} % Organization
    {Vancouver, BC} % Location 
    {May 2022 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities   
        \item {Worked on the FortiOS team developing and debugging front-end code to write production-ready code using \textbf{Angular} and \textbf{Angularjs}.}        
        \item {Collaborated and used advanced git workflows with a team of 50 developers.}         
        \item {Developed using the \textbf{Linux} operating system, \textbf{TypeScript}, and \textbf{JavaScript}.}    
        \item {Acquired deep knowledge involving networking, firewalls, and network security.}  
      \end{cvitems}
    } 

%---------------------------------------------------------
  \cventry
    {full stack developer intern} % Job title
    {Royal Bank of Canada} % Organization
    {Toronto, ON (Remote)} % Location 
    {Sep 2021 - May 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities  
        \item {Engineered an AutoML pipeline from scratch involving imputation, categorical encoding, feature engineering, model selection, and hyperparameter optimization using \textbf{Python, Apache Spark, Apache Openshift, Kubernetes, and H2O}.}  
        \item {Sped up the model training and hyperparameter tuning process by 50\% achieving better accuracy than manually trained models.}    
        \item {Adapted to a vendor platform (\textbf{Palantir Foundry}) with a lack of documentation quickly.} 
        \item {Invented a new way to add support for python libraries in \textbf{Palantir Foundry}. Thus, helping the data science team immensely.} 
      \end{cvitems}
    }

% \vspace{-4.0mm}

% \vspace{-2.0mm}

%---------------------------------------------------------
  \cventry
    {research assistant} % Job title
    {University of British Columbia} % Organizatiochrome.storage.local.set({"noPdfViewer": 1})n
    {Kelowna BC} % Location
    {Jan 2021 - May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed a new UI with a team of developers for a website used by university professors to make teams for group projects.}     
        \item {Advocated for WCAG adherence to develop a new UI.}     
        \item {Utilized the following tech stack:  \textbf{Django, PostgreSQL, Docker, Redis.}}
      \end{cvitems}
    }

% \vspace{-2.0mm}

% \vspace{-4.0mm}
%---------------------------------------------------------
  \cventry
    {teaching assistant} % Job title
    {University of British Columbia} % Organization
    {Kelowna, BC} % Location
    {Jan 2020 - May 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Instructed 2 classes of 20-30 students teaching data structures and algorithm concepts in \textbf{Java}.} 
        \item {Worked in a team of 5 to mark assignments/exams and assist students during classes.} 
      \end{cvitems}
    }


\end{cventries}
