
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Technical Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}



% \vspace{-2.0mm}
  \cventry
    {react, redux, node, django, postgresql, mongodb, rabbitmq, s3, docker, redis } % Tech stack
    {Summer 2021 Capstone Project | Full Stack Project}  % project name
    {} % url 
    {} 
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {worked with a client and helped }
        \item {Integrated Redux for global state management and error handling.}
        \item {Utilized Babel and Webpack in the development of the app to support legacy browsers. }
      \end{cvitems}
    }
%---------------------------------------------------------

% \vspace{-2.0mm}
  \cventry
    {react, redux, rest, babel, webpack} % Tech stack
    {Pokedex | React SPA}  % project name
    {https://pokedexme.vercel.app/} % url 
    {} 
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Fetched and displayed data from a REST API using a frontend powered by React.}
        \item {Integrated Redux for global state management and error handling.}
        \item {Utilized Babel and Webpack in the development of the app to support legacy browsers. }
      \end{cvitems}
    }

% \vspace{-2.0mm}
  \cventry
    {react, google cloud services, node.js, aws amplify} % Tech stack
    {Remarrk | Full Stack Project}  % project name
    {https://bit.ly/31uafpE} % url 
    {} 
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web app which uses React for the frontend, Express on the backend and firebase for database and authentication, while being Hosted using AWS Amplify.}
      \end{cvitems}
    }

  % \cventry
  %   {react, google cloud services, node.js, aws amplify} % Tech stack
  %   {Remarrk | Full Stack Project}  % project name
  %   {https://devpost.com/software/remarrk/} % url 
  %   {} 
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Web app which uses React for the frontend, Express on the backend and firebase for database and authentication, while being Hosted using AWS Amplify.}
  %     \end{cvitems}
  %   }

% \vspace{-2.0mm}
  \cventry
    {next.js, react, tailwindcss} % Job title
    {Covid.army | Open Source} % Organization
    {https://covid.army} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed and helped develop Covid.army, an Open Source website devoted to providing info on Covid related resources in India. The website was visited by over 3 million people.} 
      \end{cvitems}
    }
% \vspace{-2.0mm}
  \cventry
    {pandas, numpy, scikit-learn} % Job title
    {Sentiment-Analysis | Machine learning} % Organization
    {https://bit.ly/303OIDq} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented several machine learning models using Natural language processing (NLP) including Gradient-boost, XGboost, ADA-boost to classify pieces of text as either positive or negative. The best model had an accuracy of over 92\% on test data.} 
      \end{cvitems}
    }

% \vspace{-2.0mm}
  \cventry
    {Java} % Job title
    {Game AI | Aritifical Intelligence Project} % Organization
    {https://bit.ly/3H0iB8H} % Date(s)
    {} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with a team to implement a game AI for game of the amazons. The game agent used Minimax search with Alpha beta pruning and iterative deepening to win. } 
        \item {Our agent placed sixth out of twenty five.} 
      \end{cvitems}
    }
\end{cventries}
